Does personal relevance attenuate citizens' persuasion by government branding? Evidence from a survey experiment on air-pollution policy

### 2019-07-25 paper3_revision_tables.Rmd
Add files via upload

#labels of vars
vars.lab = c(
         "Gender (Woman=1)",
         "Age",
         "Trust in government ministries",
         "Political Ideology (10 = extreme left)",
         "Education",
         "Income (5=high)",
         "Parents",
         "Parents of young children (under 12)",
         "Interest in environmental issues",
         "Air-pollution policy",
         "Recycling policy"
)

@@

t3.center %>%
    filter(str_detect(variable,"policy")==F) %>%
    kable(col.names = c("",
                    str_c("All sample (n=",SVIVA2_01_center %>% nrow(),")"),
                    str_c("No symbols (n=",SVIVA2_01_center %>% filter(SYMBOL==0) %>%  nrow(),")"),
                    str_c("Fake symbols (n=",SVIVA2_01_center %>% filter(SYMBOL==1) %>%  nrow(),")"),
                    str_c("Real symbols (n=",SVIVA2_01_center %>% filter(SYMBOL==2) %>%  nrow(),")"),
                    "f-test",
                    str_c("Strong Air-pollution (Weak recycling) (n=",SVIVA2_01_center %>% filter(INFORMATION_air==1) %>% nrow(),")"),
                    str_c("Weak air-pollution (Strong recycling) (n=",SVIVA2_01_center %>% filter(INFORMATION_air==0) %>% nrow(),")"),
                     "t-test",
                    str_c("Treatment (n=",SVIVA2_01_haifa %>% filter(RELEVANCE_exp==1) %>% nrow(),")"),
                    str_c("Control (n=",SVIVA2_01_haifa %>% filter(RELEVANCE_exp==0) %>% nrow(),")"),
                    "t-test"))%>%
  kable_styling(bootstrap_options = c("condensed"),
                full_width = F,
                position = "left",
                font_size = 9) %>%
  add_header_above(c(" " = 2, 
                     "Symbols groups" = 4,  
                     "Information groups" = 3, 
                     "Relevance groups" = 3))
```
<font size="0.5">

@@

```{r, fig.width=8,fig.height=4}
SVIVA2_01 %>%
  select(AREA_names,
         RELEVANCE_air_obs,
         RELEVANCE_waste_obs) %>% 
  gather(key = policy, value = relevance, -AREA_names) %>%
  mutate(policy = Recode(policy,"'RELEVANCE_air_obs'='Air-pollution policy';'RELEVANCE_waste_obs'='Recycling policy'")) %>% 
ggplot(aes(AREA_names,relevance))+ 
  theme_tufte()+
  geom_boxplot(width=0.25,color="gray70")+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
               fun.args = list(mult = 1.96),
               width=0.05,size=0.5) + 
  stat_summary(fun.y = mean, geom = "point", size=1.6)+
  facet_grid(~policy)+
  xlab("")+
  scale_y_continuous(name = "Perceived personal relevance",limits=c(1,7),breaks = seq(1,7,by=1))
```
<font size="0.5">

@@

`r figure.x=figure.x+1`**Figure `r figure.x`: The distribution of Trust in air-pollution across the different conditions of symbols and information**

```{r, fig.width=8, fig.height=4}
p1 <- SVIVA2_01_comb %>%
ggplot(aes(SYMBOL_n,TRUST_air_INDEX))+ 
  theme_tufte()+
  geom_boxplot(width=0.25,color="gray70")+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
               fun.args = list(mult = 1.96),
               width=0.05,size=0.5) + 
  stat_summary(fun.y = mean, geom = "point", size=1.6)+
  stat_summary(fun.y = mean, geom = "line", size=0.6, aes(group = 1))+
  scale_x_discrete(name = "",labels = c("No symbols","Fake symbols","Real symbols"))+
  scale_y_continuous(name = "Trust in air-pollution policy",limits=c(1,7),breaks = seq(1,7,by=1))+
  ggtitle("Symbols")

@@

```{r, fig.width=8}
p1 <- SVIVA2_01_comb %>%
  filter(policy=="TRUST_air_INDEX") %>% 
ggplot(aes(factor(SYMBOL_n),trust,shape=factor(AREA_names)))+ 
  theme_tufte()+
  #geom_boxplot(width=0.25,color="gray70")+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
               fun.args = list(mult = 1.96),
               width=0.1,size=0.5,position=position_dodge(0.1),color="gray70") + 
  stat_summary(fun.y = mean, geom = "point", size=1.6,position=position_dodge(0.1))+
  stat_summary(fun.y = mean, geom = "line", size=0.6, aes(group = AREA_names,linetype=AREA_names),position=position_dodge(0.1),alpha=0.8)+
  scale_shape_manual(guide=F, values=c(19,1))+
  scale_linetype_manual(guide=F, values=c(1,4))+
  scale_x_discrete(name="",labels=c("No symbols","Fake symbols","Real symbols"))+
  scale_y_continuous(name = "Trust in air-pollution policy",breaks = seq(1,7,by=0.5))+
  ggtitle("Symbols")

@@

`r table.x=table.x+1`**Table `r table.x`: Regression analyses – Trust in Air-pollution policy.**

@@

stargazer(mod_air_1.1,mod_air_null,
          mod_air_1.2,mod_air_null,
          mod_air_1.3, mod_air_null,
          mod_air_1.4, mod_air_null,
          type = "html",
          se  = list(mod_air_1.1.robust_se,NULL,
                     mod_air_1.2.robust_se,NULL,
                     mod_air_1.3.robust_se,NULL,
                     mod_air_1.4.robust_se,NULL),
          style = "apsr",
          report = "vcsp",
          omit.stat = c("rsq","ser", "f"),
          initial.zero = FALSE,
          column.labels   = str_c("(1.",1:4,")"),
          column.separate = c(2,2,2,2),
          dep.var.labels="Trust in air-pollution policy",
          omit = control.vars,
          covariate.labels=c("Real symbols",
                             "Fake-symbols",
                             "Weak Information",
                             "Area (0=Haifa Bay; 1=center)",
                             "Area x Real symbols",
                             "Area x Fake symbols",
                             "Area x Weak Information"),
          p.auto = F,
          add.lines = list(
                           c("Controls","No","","No","","No","","Yes",""),
                           c("F Statistic", 
                             mod_air_1.1.wald_results[2,3] %>% round(2),NA,
                             mod_air_1.2.wald_results[2,3] %>% round(2),NA,
                             mod_air_1.3.wald_results[2,3] %>% round(2),NA,
                             mod_air_1.4.wald_results[2,3] %>% round(2),NA)),
          notes = "*Notes*: In all regression tables, entries are nonstandardized OLS-regression coefficients. Robust standard errors are in parentheses and *p-values* (two-tailed) are reported. The reference category for the symbols manipulation conditions is the control (no symbols).",
          notes.append = FALSE)

@@

stargazer(mod_relevance_1.1,mod_relevance_null,
          mod_relevance_1.2,mod_relevance_null,
          mod_relevance_1.3, mod_relevance_null,
          type = "html",
          se  = list(mod_relevance_1.1.robust_se,NULL,
                     mod_relevance_1.2.robust_se,NULL,
                     mod_relevance_1.3.robust_se,NULL),
          style = "apsr",
          report = "vcsp",
          omit.stat = c("rsq","ser", "f"),
          initial.zero = FALSE,
          column.labels   = str_c("(3.",1:4,")"),
          column.separate = c(2,2,2),
          dep.var.labels="Trust in air-pollution policy",
          omit = control.vars,
          covariate.labels=c("Real symbols",
                             "Fake-symbols",
                             "Weak Information",
                             "Relevance treatment",
                             "Relevance treatment x Real symbols",
                             "Relevance treatment x Fake symbols",
                             "Relevance treatment x Weak Information"),
          p.auto = F,
          add.lines = list(
                           c("Controls","No","","No","","Yes",""),
                           c("F Statistic", 
                             mod_relevance_1.1.wald_results[2,3] %>% round(2),NA,
                             mod_relevance_1.2.wald_results[2,3] %>% round(2),NA,
                             mod_relevance_1.3.wald_results[2,3] %>% round(2),NA)),
          notes = "",
          notes.append = FALSE)
```

>>>>

#labels of vars
vars.lab = c(
         "Gender (Woman=1)",
         "Age",
         "Trust in government ministries",
         "Political Ideology (10 = extreme left)",
         "Education",
         "Income (5=high)",
         "Parents",
         "Parents of young children (under 12)",
         "Interest in environmental issues",
         "Haifa Bay air-pollution policy",
         "Recycling policy"
)

@@

t3.center %>%
    filter(str_detect(variable,"policy")==F) %>%
    kable(col.names = c("",
                    str_c("All sample (n=",SVIVA2_01_center %>% nrow(),")"),
                    str_c("No symbols (n=",SVIVA2_01_center %>% filter(SYMBOL==0) %>%  nrow(),")"),
                    str_c("Fake symbols (n=",SVIVA2_01_center %>% filter(SYMBOL==1) %>%  nrow(),")"),
                    str_c("Real symbols (n=",SVIVA2_01_center %>% filter(SYMBOL==2) %>%  nrow(),")"),
                    "f-test",
                    str_c("Strong Air-pollution (Weak recycling) (n=",SVIVA2_01_center %>% filter(INFORMATION_air==1) %>% nrow(),")"),
                    str_c("Weak air-pollution (Strong recycling) (n=",SVIVA2_01_center %>% filter(INFORMATION_air==0) %>% nrow(),")"),
                     "t-test",
                    str_c("Treatment (n=",SVIVA2_01_center %>% filter(RELEVANCE_exp==1) %>% nrow(),")"),
                    str_c("Control (n=",SVIVA2_01_center %>% filter(RELEVANCE_exp==0) %>% nrow(),")"),
                    "t-test"))%>%
  kable_styling(bootstrap_options = c("condensed"),
                full_width = F,
                position = "left",
                font_size = 9) %>%
  add_header_above(c(" " = 2, 
                     "Symbols groups" = 4,  
                     "Information groups" = 3, 
                     "Relevance groups" = 3))
```
<font size="0.5">

@@

```{r, fig.width=8,fig.height=4}
SVIVA2_01 %>%
  select(AREA_names,
         RELEVANCE_air_obs,
         RELEVANCE_waste_obs) %>% 
  gather(key = policy, value = relevance, -AREA_names) %>%
  mutate(policy = Recode(policy,"'RELEVANCE_air_obs'='Haifa Bay air-pollution policy';'RELEVANCE_waste_obs'='Recycling policy'")) %>% 
ggplot(aes(AREA_names,relevance))+ 
  theme_tufte()+
  geom_boxplot(width=0.25,color="gray70")+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
               fun.args = list(mult = 1.96),
               width=0.05,size=0.5) + 
  stat_summary(fun.y = mean, geom = "point", size=1.6)+
  facet_grid(~policy)+
  xlab("")+
  scale_y_continuous(name = "Perceived personal relevance",limits=c(1,7),breaks = seq(1,7,by=1))
```
<font size="0.5">

@@

`r figure.x=figure.x+1`**Figure `r figure.x`**

```{r, fig.width=8, fig.height=4}
p1 <- SVIVA2_01_comb %>%
ggplot(aes(SYMBOL_n,TRUST_air_INDEX))+ 
  theme_tufte()+
  geom_boxplot(width=0.25,color="gray70")+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
               fun.args = list(mult = 1.96),
               width=0.05,size=0.5) + 
  stat_summary(fun.y = mean, geom = "point", size=1.6)+
  stat_summary(fun.y = mean, geom = "line", size=0.6, aes(group = 1))+
  scale_x_discrete(name = "",labels = c("No symbols","Fake symbols","Real symbols"))+
  scale_y_continuous(name = "Trust in Haifa Bay air-pollution policy",limits=c(1,7),breaks = seq(1,7,by=1))+
  ggtitle("Symbols")

@@

```{r, fig.width=8}
p1 <- SVIVA2_01_comb %>%
  filter(policy=="TRUST_air_INDEX") %>% 
ggplot(aes(factor(SYMBOL_n),trust,shape=factor(AREA_names)))+ 
  theme_tufte()+
  #geom_boxplot(width=0.25,color="gray70")+
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
               fun.args = list(mult = 1.96),
               width=0.1,size=0.5,position=position_dodge(0.1),color="gray70") + 
  stat_summary(fun.y = mean, geom = "point", size=1.6,position=position_dodge(0.1))+
  stat_summary(fun.y = mean, geom = "line", size=0.6, aes(group = AREA_names,linetype=AREA_names),position=position_dodge(0.1),alpha=0.8)+
  scale_shape_manual(guide=F, values=c(19,1))+
  scale_linetype_manual(guide=F, values=c(1,4))+
  scale_x_discrete(name="",labels=c("No symbols","Fake symbols","Real symbols"))+
  scale_y_continuous(name = "Trust in Haifa Bay air-pollution policy",breaks = seq(1,7,by=0.5))+
  ggtitle("Symbols")

@@

`r table.x=table.x+1`**Table `r table.x`: Regression analyses – Trust in Haifa Bay air-pollution policy.**

@@

stargazer(mod_air_1.1,mod_air_null,
          mod_air_1.2,mod_air_null,
          mod_air_1.3, mod_air_null,
          mod_air_1.4, mod_air_null,
          type = "html",
          se  = list(mod_air_1.1.robust_se,NULL,
                     mod_air_1.2.robust_se,NULL,
                     mod_air_1.3.robust_se,NULL,
                     mod_air_1.4.robust_se,NULL),
          style = "apsr",
          report = "vcsp",
          omit.stat = c("rsq","ser", "f"),
          initial.zero = FALSE,
          column.labels   = str_c("(1.",1:4,")"),
          column.separate = c(2,2,2,2),
          dep.var.labels="Trust in Haifa Bay air-pollution policy",
          omit = control.vars,
          covariate.labels=c("Real symbols",
                             "Fake-symbols",
                             "Weak Information",
                             "Area (0=Haifa Bay; 1=center)",
                             "Area x Real symbols",
                             "Area x Fake symbols",
                             "Area x Weak Information"),
          p.auto = F,
          add.lines = list(
                           c("Controls","No","","No","","No","","Yes",""),
                           c("F Statistic", 
                             mod_air_1.1.wald_results[2,3] %>% round(2),NA,
                             mod_air_1.2.wald_results[2,3] %>% round(2),NA,
                             mod_air_1.3.wald_results[2,3] %>% round(2),NA,
                             mod_air_1.4.wald_results[2,3] %>% round(2),NA)),
          notes = "*Notes*: In all regression tables, entries are nonstandardized OLS-regression coefficients. Robust standard errors are in parentheses and *p-values* (two-tailed) are reported. The reference category for the symbols manipulation conditions is the control (no symbols).",
          notes.append = FALSE)

@@

stargazer(mod_relevance_1.1,mod_relevance_null,
          mod_relevance_1.2,mod_relevance_null,
          mod_relevance_1.3, mod_relevance_null,
          type = "html",
          se  = list(mod_relevance_1.1.robust_se,NULL,
                     mod_relevance_1.2.robust_se,NULL,
                     mod_relevance_1.3.robust_se,NULL),
          style = "apsr",
          report = "vcsp",
          omit.stat = c("rsq","ser", "f"),
          initial.zero = FALSE,
          column.labels   = str_c("(3.",1:4,")"),
          column.separate = c(2,2,2),
          dep.var.labels="Trust in Haifa Bay air-pollution policy",
          omit = control.vars,
          covariate.labels=c("Real symbols",
                             "Fake-symbols",
                             "Weak Information",
                             "Relevance treatment",
                             "Relevance treatment x Real symbols",
                             "Relevance treatment x Fake symbols",
                             "Relevance treatment x Weak Information"),
          p.auto = F,
          add.lines = list(
                           c("Controls","No","","No","","Yes",""),
                           c("F Statistic", 
                             mod_relevance_1.1.wald_results[2,3] %>% round(2),NA,
                             mod_relevance_1.2.wald_results[2,3] %>% round(2),NA,
                             mod_relevance_1.3.wald_results[2,3] %>% round(2),NA)),
          notes = "",
          notes.append = FALSE)
```
